Development and validation of the nursing confidence in managing sedation complications scale

### 2020-09-21 manuscript.rmd
nursing open

### Introduction

It is possible that nurses may not take actions to manage sedation-related complications if they lack confidence in their abilities to complete the necessary tasks. The aim of this study was to develop the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS).

@@

An expert panel rated the relevance of an initial bank of items. Items with a content validity index of less than 0.78 were revised or deleted. An online survey containing items from the revised scale was distributed to nurses who were members of five different specialty nursing associations in Australia. Principal axis factoring and promax rotation was used for factor extraction. Multivariable linear regression was used to identify associations between scale scores and nurses' experience and education regarding sedation. Internal consistency was calculated to examine reliability. Responsiveness was evaluated using a pre-test post-test design with a sample of nurses who completed a sedation education program.

@@

Pre-specified criteria for content validity was met for 34 items. Responses from 228 nurses who participated in the online survey were analysed. An 18-item, 3-factor solution was identified as the most parsimonious solution, with subscales accounting for 65.6% of the variance. Cronbach's alpha for the scale (`r round(targets::tar_read(reliability_total)$total$std.alpha, 2)`) and subscales was high (\>0.85). There were significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and work environment (critical care/anaesthesia versus procedural/operating theatre). The change in NC-MSCS scores reported by the 31 nurses who participated in the pre-test post-test study increased significantly from before to after sedation training (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)}-{round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`). Change in NC-MSCS was correlated with the change in overall confidence and knowledge about managing sedation complications.

### Conclusion

The NC-MSCS is a valid and reliable instrument, which could be used to guide and inform sedation training programs and competency assessments.

@@

The NC-MSCS was developed and validated through three phases. Content validity of the items was evaluated in the first phase with input from an expert panel of clinicians with expertise in procedural sedation. In the second phase, a survey study was undertaken for item reduction and to evaluate the structural validity of the scale. In the third phase, responsiveness was evaluated using a pre-test post-test design. Ethical approval was provided by the Queensland University of Technology Human Research Ethics Committee (61986 and 56161).

@@

>>>>

### Aim

To develop the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS).

### Design

A multi-phased approach was used to inspect the psychometric properties of the scale.

@@

Content validity was assessed by an expert panel. Exploratory factor analysis was used for item reduction and multivariable linear regression was used to explore construct validity. Responsiveness was evaluated using a pre-test post-test design.

@@

Pre-specified criteria for content validity was met for 34 items. Responses from 228 nurses who participated in the online survey were analysed. An 18-item, 3-factor solution was identified, with subscales accounting for 66% of the variance. Cronbach's alpha for the scale (`r round(targets::tar_read(reliability_total)$total$std.alpha, 2)`) and subscales was high (\>0.85). There were significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and work environment. NC-MSCS scores from a sample of 31 nurses increased significantly from before to after sedation training (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)}-{round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`).

@@

The NC-MSCS was developed and validated through three phases. Content validity of the items was evaluated in the first phase with input from an expert panel of clinicians with expertise in procedural sedation. In the second phase, a survey study was undertaken for item reduction and to evaluate the structural validity of the scale. In the third phase, responsiveness was evaluated using a pre-test post-test design. The STROBE checklist was used to guide the reporting of results.

@@

### Ethics

Ethical approval was provided by the Queensland University of Technology Human Research Ethics Committee (61986 and 56161).
